Reply to reviewers concerning submission AAA-D-19-00080: "Estimation of the perceived time of presence of sources in urban acoustic environments using deep learning techniques"

### 2019-10-07 paper/submitted/coverLetter.tex
v2 ready to submit

As a preamble, we would like to thank the editor and the reviewer for their comments and suggestions. Following these comments, we made several changes to the article including a modification of the structure of the document, which are summarized here. The next sections list our answers to each of the reviewer’s comments, with references to the revised manuscript (page, column, and paragraph) where appropriate.

@@

$\rightarrow$ Statistics used to simulate sound scenes are based on 74 recordings of which the 19 used for replication are a subset. Section 2.1 has been rewritten to describe more extensively this reference database. To generate more diverse scenarios the variance of all statistics is further increased. However, we acknowledge that the model needs to be evaluated on a more complete and representative set of recordings to assess fully its generalization capabilities.

@@

$\rightarrow$ In this paper, we chose to focus on the three main categories of sources that are known to impact soundscape quality. When applying the proposed approach to a specific environment, the taxonomy of sound sources needs to be extended accordingly. This is now discussed in Section 5. Also, as is now emphasized in the Introduction and Section 2 the present study considers the point of view of pedestrians, which is vastly different from that of residents in terms of sources of interest.\\
The quality of the pleasantness model obtained from time of presence approximations is bound by the listening test corpus, and thus mostly by the contents of simulated scenes. Section 4.1 discusses possible causes to the absence of other sources in the model. However, this model is not intended as a contribution but rather as a intermediary to show that presence predictions from the deep learning architecture are accurate enough to estimate more abstract perceptual notions.

@@

$\rightarrow$ The main objective of this work is the prediction of the perceived time of presence of sources of interest for the perceptual characterization of soundscapes. We study the estimation of pleasantness as an application, but the developped method could also be used to predict other quality descriptors or in mapping applications (eg.~\cite{lavandier2016}). The structure of the paper has been rearranged to emphasize this aim.

@@

$\rightarrow$ In this study no background noise was added in a controlled manner. However, some background noise is present in the isolated samples used to simulate sound scenes. Particularly, each scene contains at least one background source for which recordings obtained on Freesound are used. These recordings were selected to be representative of the source but were not cleaned through pre-processing, leading to (uncontrolled) background noise being present to an extent in each simulated scene.

@@

$\rightarrow$ This work is placed in the context of a monitoring application through sensor networks in urban areas, for which using features computed on fine time scales may not be viable in the long term due to storage and privacy concerns. Though information on smaller time scales would be more appropriate to detect sound events (from a few milliseconds for birds to tens of milliseconds for speech), this motivates our choice to operate on the third-octave spectrum with 125ms hop size, which is typical in monitoring studies. This is now discussed in the introduction.

@@

$\rightarrow$ The abstract has been revised to reduce background information in favor of the description and results of the current study.

@@

$\rightarrow$ Many studies dealing with the environmental acoustic quality are associated with duration of acoustic measurements ranging from few seconds for the shorter~\cite{paulsen1997, brambilla2006} to fifteen minutes~\cite{kuwano1997, decoensel2007} and even to eighty minutes~\cite{namba1988}. Due to the limited duration of perceptual tests because of the fatigue, stimuli between 30s and 1mn are often prefered for laboratory tests.

@@

$\rightarrow$ The aim of this work is to determine wether a deep learning architecture can identify active sound sources in polyphonic urban sound environments from typical monitoring measurements (third-octave spectra). It is motivated by the fact that the composition of sound environments has a known influence on the perception of pedestrians, but is currently not explicitely studied in monitoring applications based on sensor networks. We achieve this goal by learning on labels approximating the perceived time of presence, which can be obtained in an automatic way if the ground truth source contributions in the training set is known. Pleasantess prediction is studied here as an application to assess the usefulness of the proposed approach.\\
The structure of the manuscript has been revised to clearly expose the process of this work:
\begin{itemize}
\item Section 2 details the deep learning dataset construction, its validation through a listening test and the choice of acoustic indicator for its automatic annotation,
\item Section 3 presents the training and results of the source detection deep learning model,
\item Section 4 applies this model to pleasantness estimation.
\end{itemize}

@@

$\rightarrow$ The claim that the European Comission 2002/49/EC directive was aimed at urban planning has been removed from the introduction.

@@

$\rightarrow$ Explications for the main equations in the manuscript have been added (eq. 1-3). Specifically, in eq. 1 the derivation is applied once on each dimension of the third-octave spectrum (hence the term second derivative), which underlines variations in time and frequency.

@@

$\rightarrow$ The structure of the paper has been changed to better link different parts of the study. Section 2 presents the generation of a large simulated dataset with 400 sound scenes for training a source detection model and an additional (independant) 200 scenes for its evaluation. A third corpus containing 100 sound scenes including 75 simulated, 19 replicated and 6 recordrd, is constructed in Section 2.2 as part of a listening test to assess the change in perception in simulated scenes and to obtain subjective evaluations useful in the rest of the paper. In Section 2.3, the listening test results motivate the choice of indicator used to automatically annotate the perceived time of presence on the 600 total scenes used in the machine learning approach.

@@

$\rightarrow$ Additional explications were added to equations 5-11 (now 5-8), and the procedure used to obtain baseline models from perceptual and acoustical parameters through multivariate linear regressions has been detailed in Section 4.1. All statistical analyses are conducted using Matlab and its statistical toolbox (code is available) and the machine learning part is implemented in the Pytorch framework. This is now stated where applicable.

>>>>

As a preamble, we would like to thank the editor and the reviewers for their comments and suggestions. Following these comments, we made several changes to the article including a modification of the structure of the document, which are summarized here. The next sections list our answers to each of the reviewer’s comments, with references to the revised manuscript (page, column, and paragraph) where appropriate.

@@

$\rightarrow$ Statistics used to simulate sound scenes are based on 74 recordings of which the 19 used for replication are a subset. Section 2.1 has been rewritten to describe more extensively this reference database. To generate more diverse scenarios the variance of all statistics is next further increased. However, we acknowledge that the model needs to be evaluated on a more complete and representative set of recordings to assess fully its generalization capabilities.

@@

$\rightarrow$ In this paper, we chose to focus on the three main canonical categories of sources that are known to impact soundscape quality. When applying the proposed approach to a specific environment, the taxonomy of sound sources needs to be extended accordingly. This is now discussed in Section 5. Also, as now emphasized in the Introduction and Section 2, the present study considers the point of view of pedestrians, which is vastly different from that of residents in terms of sources of interest.\\
The quality of the pleasantness model obtained from time of presence approximations is bound by the listening test corpus, and thus mostly by the contents of simulated scenes. Section 4.1 discusses possible causes to the absence of other sources in the model. However, this model is not intended as a contribution but rather as a mean to show that presence predictions from the deep learning architecture are accurate enough to estimate useful and more abstract perceptual indicators.

@@

$\rightarrow$ The main objective of this work is the prediction of the perceived time of presence of sources of interest for the perceptual characterization of soundscapes. We study the estimation of pleasantness as an application, but the developed method could also be used to predict other quality descriptors or in mapping applications (eg.~\cite{lavandier2016}). The structure of the paper has been rearranged to emphasize this aim.

@@

$\rightarrow$ In this study no background noise was added in a controlled manner. However, some background noise is present in the isolated samples used to simulate sound scenes. Particularly, each scene contains at least one background source for which recordings obtained on Freesound are used. These recordings were selected to be representative of the source but were not cleaned through pre-processing, leading to (uncontrolled) background noise being present to some extent in each simulated scene.

@@

$\rightarrow$ Information on smaller time scales would indeed be more appropriate to detect sound events (from a few milliseconds for birds to tens of milliseconds for speech). Though, this work is placed in the context of a monitoring application through sensor networks in urban areas, for which using features computed on fine time scales may not be viable in the long term due to storage and privacy concerns. This motivates our choice to operate on the third-octave spectrum with 125ms hop size, which is typical in monitoring studies. This is now discussed in the introduction.

@@

$\rightarrow$ The abstract has been revised to reduce background information in favor of the description of the contributions and results of the current study.

@@

$\rightarrow$ Many studies dealing with the environmental acoustic quality are associated with duration of acoustic measurements ranging from few seconds for the shorter~\cite{paulsen1997, brambilla2006} to fifteen minutes~\cite{kuwano1997, decoensel2007} and even to eighty minutes~\cite{namba1988}. Due to the limited duration of perceptual tests because of the fatigue, stimuli between 30 seconds and 1 minute are often preferred for laboratory tests.

@@

$\rightarrow$ The aim of this work is to determine wether a deep learning architecture can identify active sound sources in polyphonic urban sound environments from typical monitoring measurements (third-octave spectra). It is motivated by the fact that the composition of sound environments has a known influence on the perception of pedestrians, but is currently not explicitly studied in monitoring applications based on sensor networks. We achieve this goal by learning on labels approximating the perceived time of presence, which can be obtained in an automatic way if the ground truth source contributions in the training set is known. Pleasantness prediction is studied here as an application to assess the usefulness of the proposed approach.\\
The structure of the manuscript has been revised to clearly expose the contributions of this work:
\begin{itemize}
\item Section 2 details the deep learning dataset construction, its validation through a listening test and the choice of acoustic indicator for its automatic annotation,
\item Section 3 presents the training and results of the source detection deep learning model,
\item Section 4 applies this model to pleasantness estimation.
\end{itemize}

@@

$\rightarrow$ The claim that the European Commission 2002/49/EC directive was aimed at urban planning has been removed from the introduction.

@@

$\rightarrow$ Explanations for the main equations in the manuscript have been added (eq. 1-3). Specifically, in eq. 1 the derivation is applied once on each dimension of the third-octave spectrum (hence the term second derivative), which underlines variations in time and frequency.

@@

$\rightarrow$ The structure of the paper has been changed to better link different parts of the study. Section 2 presents the generation of a large simulated dataset with 400 sound scenes for training a source detection model and an additional (independent) 200 scenes for its evaluation. A third corpus containing 100 sound scenes including 75 simulated, 19 replicated and 6 recorded, is constructed in Section 2.2 as part of a listening test to assess the change in perception in simulated scenes and to obtain subjective evaluations useful in the rest of the paper. In Section 2.3, the listening test results motivate the choice of the indicator used to automatically annotate the perceived time of presence on the 600 total scenes used in the machine learning approach.

@@

$\rightarrow$ Additional explications were added to equations 5-11 (now 5-8), and the procedure used to obtain baseline models from perceptual and acoustical parameters through multivariate linear regressions has been detailed in Section 4.1. All statistical analyses are conducted using Matlab and its statistical toolbox (code is made available on the companion website) and the machine learning part is implemented in the Pytorch framework (also available). This is now stated where applicable.
